Daily goals

### 2020-06-26 2-body.Rmd
more intro

From molecular data to alignments and phylogenies, public biological data repositories such as the GenBank database [@benson2000genbank; @wheeler2000database], the TreeBASE repository [@piel2009treebase] and the Open Tree of Life curating system [@mctavish2015phylesystem], are still accumulating data.

@@

Pipelines have been an important incorporation to the field of phylogenetics in many ways, particularly because they represent a clear step towards reproducibility in the field. In contrast, most published phylogenies have been infered using homology hypotheses that have been curated "by hand" [@morrison2009would].
What explains this preference? aka the discordance between the genomics approach (a gazillion markers poorly aligned, but the amount of data will overcome errors in alignment) and the classic phylogenetics approach (few markers thoughtfully curated).
On one hand, there are concerns about the use of automated pipelines in phylogenetics.
Concerns I think people have about these tools:
- Errors in identification of sequences
- Little control at different steps of the process
- Too much of a black box? Most of these phylogenies are being constructed by people learning about the methods (aka students), so they want to know what is going on at each step and end up doing it manually.
-
It has also been suggested that manual curation of classic and genomic alignments produces better phylogenetic reconstructions [@fragoso2017pilot].

@@

Ultimately, linkage of original alignment with its corresponding phylogeny has to be done by a human curator.
Moreover, each one of these data repositories follow their own system for taxon identification. A real challenge is to find an effective way to link data from across databases that belongs to the same taxon.
OToL's metadata system incorporates taxon identifiers from a variety of taxonomies and repositories, including the NCBI taxonomy, GBIF, etc.

>>>>

From molecular data to alignments and phylogenies, public biological data resources such as the GenBank database [@benson2000genbank; @wheeler2000database], the TreeBASE repository [@piel2009treebase] and the Open Tree of Life curating system [@mctavish2015phylesystem], are still accumulating data and there is no straightforward way to automatically connect data belonging to the same taxon from these various resources.

@@

Pipelines have been an important incorporation to the field of phylogenetics in many ways, particularly because they represent a clear step towards reproducibility. In contrast, most published phylogenies have been infered using homology hypotheses that have been curated "by hand" [@morrison2009would].
There seems to be a preference of the classic phylogenetics approach (few markers thoughtfully curated) over the genomics approach (a massive amount of DNA markers, potentially poorly aligned, but the amount of data will overcome errors in the alignment).

On one hand, there are concerns about the use of automated pipelines in phylogenetics.
Concerns I think people have about these tools:
- Errors in identification of sequences
- Little control at different steps of the process
- Too much of a black box? Most of these phylogenies are being constructed by people learning about the methods (aka students), so they want to know what is going on at each step and end up doing it manually.

It has also been suggested that manual curation of classic alignments produces better phylogenetic reconstructions and it has been demonstrated for genomic alignments [@fragoso2017pilot].

@@

Ultimately, linkage of original alignment with its corresponding phylogeny has to be done by a human curator.
Moreover, each one of these data repositories follow their own system for taxon identification, posing a real challenge to automatically link data from across databases that belong to the same taxon.
OToL's metadata system incorporates taxon identifiers from a variety of taxonomies and repositories, including the NCBI taxonomy, GBIF, etc.

### 2020-06-26 _TODO.Rmd
more intro

>>>>

- [ ] intro: challenge in connecting different parts of the database with other databases that might refer to the same thing. For example taxon ids represent onw challenge in this sense, but it has been solved by the otol taxonomy project. Othe rchallenge is the study ids. This is not fully resolved yet by otol, but only partially by linking to the alignment repo.
- [ ] intro: programatic access.
